SIR Model With Testing Flows and Isolation

### 2020-10-27 codes/ali_test_sir.Rmd
updated analysis and sim

1- What combination of testing intensity, $t$, and isolation, $\eta_w$ and $\eta_t$, will result in $R_0 <1$?

@@

- Assume there are 3 groups of individuals: $S$, $I$ and $R$.
- Each group splits into 4 subgroups to incorporate the testing mechanism, so overall the model framework has 12 compartments as follows. $S_u,$ $S_n$, $S_p$, $S_t$, $I_u$, $I_n$, $I_p$, $I_t$, $R_u$, $R_n$, $R_p$, $R_t$.
- Further, assume that (1) a perfectly specific test, i.e. no false positives, then $S_p$ and $S_t$ are always zero (2) there are two 'integrator' or 'accumulator' compartments, $N$ and $P$, to collect cumulative reported negative or positive tests.

## Per Capita Rate of Flow from Untested to Positive or Negative Compartments

- $t$: testing intensity with dimension of $1/time$.
- $\omega$: the rate of *onward flow* from the awaiting positive compartment, $p$, to reported/tested compartment, $t$, or from awaiting negative compartment, $n$, back to $u$.  It has units of $1/time$.

- Note: The complicated part is the flow rate from $Z_u$ to $Z_n$, $Z_p$.  The (total, not per capita) flow from $Z_u$ to $Z_n$ is $t (1-P_Z) F(W_Z) Z_u$, from $Z_u$ to $Z_p$ is $t P_Z F(W_Z) Z_u$. Where, $P_Z$ is the probability of positive test.

- At the simplest $F(W_Z)=W_Z$.  The flows from $Z_n$ to $Z_u$ and $Z_p$ to $Z_t$ are $\omega Z_n$ and $\omega Z_p$ respectively. We are using a dimensionless scaling where $F(W_Z) = (W_Z \cdot N_0)/\sum_{Z'} \left( W_{Z'} {Z'}_{u} \right)$, i.e. the denominator is the sum of the product of the weights and the current occupancy of the untested compartments.

## Model

![](../pix/sir_test1.jpg)

Let the force of infection $\Lambda=\beta \frac{(I_u+\eta_w I_n+\eta_w I_p+ \eta_t I_t)}{N_0}$, where $\eta$ is the isolation parameter with the following assumptions:

(1) All susceptible individuals are exposed to all infectious individuals regardless of the group factor. 
(2) $\eta_t<\eta_w$, i.e., the awaiting individuals for test results have higher transmission probability than the reported individuals. 
(3) The scaling parameter is defined as $sc = t N_0/(W_s S_u + W_i I_u + W_r R_u)$ and $F_s = sc \times W_s$, $F_i=sc \times W_i$ and $F_r = sc\times W_r$.

The model is
\begin{align}
\label{mod:1}
1)\ d S_u/dt &= -\Lambda S_u - F_s S_u + \omega S_n \\
2)\ d S_n/dt &= -\Lambda S_n + F_s S_u - \omega S_n \\
3)\ d I_u/dt &= \Lambda S_u - F_i I_u + \omega I_n  - \gamma I_u  \\
4)\ d I_n/dt &= \Lambda S_n + (1-P_i) F_i I_u - \omega I_n -\gamma I_n \\
5)\ d I_p/dt &= P_i F_i I_u - \omega I_p -\gamma I_p \\
6)\ d I_t/dt &= \omega I_p - \gamma I_t  \\
7)\ d R_u/dt &= \gamma I_u - F_r R_u + \omega R_n \\
8)\ d R_n/dt &= \gamma I_n + (1-P_r) F_r R_u - \omega R_n  \\
9)\ d R_p/dt &= \gamma I_p + P_r F_r R_u  - \omega R_p  \\
10)\ d R_t/dt&= \gamma I_t + \omega R_p  \\
11)\ dN/dt &= \omega (S_n + I_n + R_n)   \\
12)\ dP/dt &= \omega(I_p + R_p).
\end{align}

@@

```{r, model formulation}
sir.model <- function(time,state,params){
    unpack(as.list(c(state,params)))
    ## Force of Infection  
    Lambda <- beta * (I_u + eta_w*(I_n+I_p) + eta_t*I_t)/N0
    ## scaling the weights
    sc <- tau*t*N0/(tau*(W_s*S_u+W_i*I_u+W_r*R_u)+t*N0)
    F_s <- sc*W_s
    F_i <- sc*W_i
    F_r <- sc*W_r

@@

```{r model inputs, message=FALSE}
params <- c(N0=1000000, beta=0.8,gamma=1/3, omega=0.25, t=0.01, 
             W_s=0.01, W_i=1, W_r=0.01, #weights
             P_s=0, P_i=1, P_r=0.5, #prob of waiting for being tested positive
            eta_w=0.02, eta_t=0.01, #isolation parameter 
            s=2, #eta_w/eta_t
            tau=1
            )
class(params) <- "params_pansim"
state_init <- c(S_u=params[["N0"]], S_n=0,
                I_u=1,I_n=0,I_p=0,I_t=0,
                R_u=0,R_n=0,R_p=0,R_t=0,
                N=0,P=0)
d <- seq(0,200,by=0.1)
# Conditional stop for desolver
rootfun <- function (time, state,params) { 
  unpack(as.list(c(state,params)))
  return(I_u - 1) }
```

```{r DFE, message=FALSE}
# DFE; numerical approach
library(rootSolve)
DFE <- function(S,params){
  S_u <- S[1]
  S_n <- S[2]
  I_u <-0
  R_u<-0
  unpack(as.list(params))
  sc <- tau*t*N0/(tau*(W_s*S_u+W_i*I_u+W_r*R_u)+t*N0)
  F_s <- sc*W_s

@@

all.equal(sum(roots_dfe$root),params[["N0"]])

# DFE; analytic approach
Su_dfe <-function(params){
  unpack(as.list(params))
  a <- t
  b <- -t+(1-t/omega)*tau*W_s
  c <- -tau*W_s
  d <- b^2-4*a*c

  return(N0*2*a/(-b+sqrt(d)))
}

@@

```{r model_run, message=FALSE}
out <- as.data.frame(
  ode(
    func=sir.model,
    y=state_init,
    times= d, 
    parms=update(params,beta=2),
    # atol = 1e+1, rtol = 1e+1
    # rootfun = rootfun,
    # method="lsodar"
  )
)

@@

The Disease-Free Equilibrium, namely $E_1$, for the above SIR model is
\label{exp:dfe} $S_n^*= \frac{t}{\omega} N_0, S_u^*= N_0-S_n^*$, and $I_j=R_j=0 \ \forall j$.

@@

The Eigenvalues of $G_{11}$, are 0 and $R_0$.
```{r R0}
F_i <- function(state,params){
   unpack(as.list(c(state,params)))
  sc <- tau*t*N0/(tau*(W_s*S_u+W_i*I_u+W_r*R_u)+t*N0)
   return(sc*W_i)
 }
 # just a test
  F_i(state=state_dfe,params=update(params,t=0))

R0<-function(params){
    unpack(as.list(params))
    Su_dfe<- Su_dfe(params)
    Sn_dfe<- N0-Su_dfe
    F_i <- tau*t*N0*W_i/(tau*(W_s*Su_dfe)+t*N0) #at DFE

@@

# R0 expression with eta_w/eta_t factored
R02<-function(params){
    unpack(as.list(params))
    Su_dfe<- Su_dfe(params)
    Sn_dfe<- N0-Su_dfe
    F_i <-tau*t*N0*W_i/(tau*(W_s*Su_dfe)+t*N0) #at DFE

@@

Can we recover $R_0=\beta/\gamma$ of the simple SIR? -yes
```{r checkings}
# checking if simple R_0 for SIR can be recovered?
# Case #1: t=0
all.equal(R0(params=update(params,t=0)), params[["beta"]]/params[["gamma"]])
# Case #2: 
all.equal(R0(params=update(params,eta_t=1,eta_w=1)), params[["beta"]]/params[["gamma"]])
```

### On Behaviour of Testing at DFE Boundry
(1) Note that once the only untested people are susceptibles, the FoI will be $\Lambda=0$, testing rate $F_s=t N_0/S_u$. Thus, eq(1) of the model will be $d S_u/dt = - t N_0 + \omega S_n$ which is a linear rate of leaving the $S_u$ compartment. That means that the testing rate will be no longer dependent on $S_u$.

### Contour plot of $R_0=1$ and interpretations approache 1
```{r contour_R0_1, message=FALSE,warning=FALSE }
 # specify the ranges
 beta  <- 0.5  ## set beta high enough to allow R0>1 in worst case
 eta_w <- seq(0,1, length.out=5)
 eta_t <- seq(0.001,0.5, length.out=5) 
 t     <- seq(0,0.01, length.out=10)
 omega <- seq(0.1,1 , length.out=10) #note omega must be > t
# s <- seq(1,2.5,length.out=10)

 df1 <- expand.grid(N0=params[["N0"]],beta=beta,gamma=params[["gamma"]],omega=omega,t=t,
                    W_s=params[["W_s"]],W_i=params[["W_i"]],W_r=params[["W_r"]],
                    P_s=params[["P_s"]],P_i=params[["P_i"]],P_r=params[["P_r"]],
                    eta_w=eta_w,eta_t=eta_t,s=params[["s"]],tau=params[["tau"]])

df2<- data.frame(df1,R0=apply(df1,1,function(params_in)R0(params=params_in)),
                      Fi= apply(df1,1,function(params_in)F_i(state=state_dfe,params=params_in)))

@@

```{r show_contours_1, width=24,height=24,message=FALSE,warning=FALSE}
p1 <- ggplot(df2,aes(x=omega,y=t,z=R0))+ theme_bw() +
    theme(panel.spacing=grid::unit(0,"lines"))
(p1
    + geom_contour_filled(breaks=pretty(unique(df2$R0),5),
                          alpha=0.5) ## breaks=0.2)
    + geom_contour(breaks=1,alpha=0.5,colour="black")
    + facet_grid(eta_w~eta_t, labeller=label_special)
    + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_fill_viridis_d(name=parse(text="R[0]"))
)
```

@@

```{r contour_R0_2, message=FALSE,warning=FALSE }
 # specify the ranges
 beta  <- 0.5  ## set beta high enough to allow R0>1 in worst case
 # eta_w <- seq(0,1, length.out=5) 
 eta_t <- seq(0.001,0.5, length.out=5) 
 t     <- seq(0,0.01, length.out=10)
 omega <- seq(0.1,1 , length.out=10) #note omega must be > t
s <- seq(1,2.5,length.out=10)

 df11 <- expand.grid(N0=params[["N0"]],beta=beta,gamma=params[["gamma"]],omega=omega,t=t,
                    W_s=params[["W_s"]],W_i=params[["W_i"]],W_r=params[["W_r"]],
                    P_s=params[["P_s"]],P_i=params[["P_i"]],P_r=params[["P_r"]],
                    eta_w=params[["eta_w"]],eta_t=eta_t,s=s,tau=params[["tau"]])

df22<- data.frame(df11,R0=apply(df11,1,function(params_in)R02(params=params_in)),
                      Fi= apply(df1,1,function(params_in)F_i(state=state_dfe,params=params_in)))

```{r show_contours_2, width=24,height=24,message=FALSE,warning=FALSE}
p11 <- ggplot(df22,aes(x=omega,y=t,z=R0))+ theme_bw() +
    theme(panel.spacing=grid::unit(0,"lines"))
(p11
    + geom_contour_filled(breaks=pretty(unique(df22$R0),5),
                          alpha=0.5) ## breaks=0.2)
    + geom_contour(breaks=1,alpha=0.5,colour="black")
    + facet_grid(s~eta_t, labeller=label_special)
    + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_fill_viridis_d(name=parse(text="R[0]"))
)
```

@@

1. $\partial{R_0}/\partial{\eta_t} \geq 0$ and $\partial{R_0}/\partial{\eta_w} \geq 0$.
2. $\partial{R_0}/\partial{t} \leq 0$; this is concluded from the Taylor expansion of $R_0$ around $t=0$ which is
$R_0 \approx \beta/\gamma + \frac{\beta t}{\omega (\omega+\gamma) \gamma^2 W_s} \Big(\gamma(\eta_w-1)(\gamma W_s+\omega W_i) + (\eta_t -1)P_iW_i \omega^2 \Big) + \mathcal{O}(t^2)$.
3. Based on the above Taylor expansion around $t=0$,
$$\partial{R_0}/\partial{\omega}=  \frac{-\beta t}{\gamma W_s\omega^2 (\gamma+\omega)^2}  (a \omega^2 + b \omega + c), $$
where $a=(\eta_w-1)W_i-(\eta_t-1)P_iW_i$, $b=2(\eta_w-1)\gamma W_s$ and $c=(\eta_w-1)\gamma^2 W_s$.
Given that $\eta_t\leq \eta_w$, it is inferred that $a\geq 0$, $b\leq 0$ and $c \leq 0$.
Let $\omega_1<0$ and $\omega_2>0$ be the roots of the quadratic expression in $\partial{R_0}/\partial{\omega}$. Thus, $\partial{R_0}/\partial{\omega}>0$ for $0<\omega<\omega_2$ and  $\partial{R_0}/\partial{\omega}<0$ for $\omega>\omega_2$.

@@

Note that $\eta_t\leq \eta_w$, i.e., reported people have a lower transmission probability than awaiting individuals. The perfect isolation/quarantine occurs when $\eta_w=\eta_t=0$ (see the upper left corner panel). Thus, we only consider the lower-triangle panels in the plot [not sure how to extract them in ggplot?].
(1) Looking at the first column of panels, there seems to be a compensatory relation between $t$ and $\omega$. i.e., higher $t$ requires smaller $\omega$ to keep R0 lower than 1. Also, for a fixed $\omega$, increasing $\eta_w$ requires higher $t$ to achieve the critical R0.
(2) A sensible result that we are expecting is $\partial{R_0}/\partial{\omega}<0$.

>>>>

1- What combination of testing intensity, $\rho$, and isolation, $\eta_w$ and $\eta_t$, will result in $R_0 <1$?

@@

### Assumptions
- Assume there are 3 groups of individuals: $S$, $I$ and $R$.
- Each group splits into 4 subgroups to incorporate the testing mechanism, so overall the model framework has 12 compartments as follows. $S_u,$ $S_n$, $S_p$, $S_t$, $I_u$, $I_n$, $I_p$, $I_t$, $R_u$, $R_n$, $R_p$, $R_t$.
- Further, assume that (1) a perfectly specific test, i.e. no false positives, then $S_p$ and $S_t$ are always zero (2) there are two 'integrator' or 'accumulator' compartments, $N$ and $P$, to collect cumulative reported negative or positive tests. 
- There is a single FoI, $\Lambda$, all groups being exposed to all others. That is, where a susceptible individual move to does not depend on who infected it.

### Parameters

```{r, out.width = "400px"}
knitr::include_graphics("../pix/sir_comp2.png")
```

- $\Lambda$: force of infection defined as $$\Lambda=\beta \frac{(I_u+\eta_w I_n+\eta_w I_p+ \eta_t I_t)}{N_0},$$ where $\beta$ is transmission rate, $\eta_w$ and $\eta_t$ are the isolation parameters for awaiting and reported individuals, respectively. We assume that $\eta_t<\eta_w$, i.e., the awaiting individuals for test results have a higher transmission probability than the reported individuals.
- $\omega$: the rate of *onward flow* from the awaiting positive compartment, $p$, to reported/tested compartment, $\rho$, or from awaiting negative compartment, $n$, back to $u$.  It has units of $1/time$.
- $\gamma$: recovery rate ($1/time$).
- $\rho$: per capita testing intensity ($1/time$).
- $\tau$: the maximum rate of testing the whole untested population ($1/time$).
- $W$: weighted number of people available for tests, defined as $W = W_s S_u + W_i I_u + W_r R_u$.
- $\sigma$: scaling parameter for testing defined as $\sigma = \frac{\tau \rho N_0}{\tau W + \rho N_0}$.
- $F_z$: Weighted testing rate defined as $F_z=\sigma W_z$. That is, $F_s = \sigma W_s$, $F_i=\sigma W_i$ and $F_r = \sigma W_r$.

**Notes:** 
- The complicated part is the flow rate from $Z_u$ to $Z_n$, $Z_p$. The (total, not per capita) flow from $Z_u$ to $Z_n$ is $\rho (1-P_z) F(W_z) Z_u$, from $Z_u$ to $Z_p$ is $\rho P_Z F(W_Z) Z_u$. Where, $P_z$ is the probability of positive test. Thus, $P_i$ represents the test accuracy. We assume $P_s=0$.
- On testing and scaling; at the simplest $F_z=W_z$.  
- JD: If this $\tau$ is fast (e.g., 1d), it should have minimal effects on the system when we're in the usual domain. Since $\tau \gg \rho$, this generally collapses to the original form. When $W$ is super-small, however, it collapses instead to $\tau$.

### Model
The model is
\begin{align}
\label{mod:1}
1)\ d S_u/dt &= -\Lambda S_u - F_s S_u + \omega S_n \\
2)\ d S_n/dt &= -\Lambda S_n + F_s S_u - \omega S_n \\
3)\ d I_u/dt &= \Lambda S_u - F_i I_u + \omega I_n  - \gamma I_u  \\
4)\ d I_n/dt &= \Lambda S_n + (1-P_i) F_i I_u - \omega I_n -\gamma I_n \\
5)\ d I_p/dt &= P_i F_i I_u - \omega I_p -\gamma I_p \\
6)\ d I_t/dt &= \omega I_p - \gamma I_t  \\
7)\ d R_u/dt &= \gamma I_u - F_r R_u + \omega R_n \\
8)\ d R_n/dt &= \gamma I_n + (1-P_r) F_r R_u - \omega R_n  \\
9)\ d R_p/dt &= \gamma I_p + P_r F_r R_u  - \omega R_p  \\
10)\ d R_t/dt&= \gamma I_t + \omega R_p  \\
11)\ dN/dt &= \omega (S_n + I_n + R_n)   \\
12)\ dP/dt &= \omega(I_p + R_p).
\end{align}

@@

```{r, model formulation}
sir.model <- function(time,state,params){
    unpack(as.list(c(state,params)))
    ## Force of Infection  
    Lambda <- beta * (I_u + eta_w*(I_n+I_p) + eta_t*I_t)/N0
    ## scaling the weights
    sigma <- tau*rho*N0/(tau*(W_s*S_u+W_i*I_u+W_r*R_u)+rho*N0)
    F_s <- sigma*W_s
    F_i <- sigma*W_i
    F_r <- sigma*W_r

@@

```{r model inputs, message=FALSE}
params <- c(N0=1000000, beta=0.8,gamma=1/3, omega=0.25, rho=0.01, 
             W_s=0.01, W_i=1, W_r=0.01, #weights
             P_s=0, P_i=1, P_r=0.5, #prob of waiting for being tested positive
            eta_w=0.02, eta_t=0.01, #isolation parameter 
            s=2, #eta_w/eta_t
            tau=1
            )
class(params) <- "params_pansim"
state_init <- c(S_u=params[["N0"]], S_n=0,
                I_u=1,I_n=0,I_p=0,I_t=0,
                R_u=0,R_n=0,R_p=0,R_t=0,
                N=0,P=0)
d <- seq(0,200,by=0.1)
# Conditional stop for desolver
rootfun <- function (time, state,params) { 
  unpack(as.list(c(state,params)))
  return(I_u - 1) }
```

```{r DFE, message=FALSE}
# DFE; numerical approach
library(rootSolve)
DFE <- function(S,params){
  S_u <- S[1]
  S_n <- S[2]
  I_u <-0
  R_u<-0
  unpack(as.list(params))
  sigma <- tau*rho*N0/(tau*(W_s*S_u+W_i*I_u+W_r*R_u)+rho*N0)
  F_s <- sigma*W_s

@@

# DFE; analytic approach

Su_dfe <-function(params){
  unpack(as.list(params))
  a <- rho
  b <- -rho+(1-rho/omega)*tau*W_s
  c <- -tau*W_s
  d <- b^2-4*a*c

  if(rho){return(N0*2*a/(-b+sqrt(d)))}
    else {return(N0)}
}

@@

```{r model_run, message=FALSE}
out <- as.data.frame(
  ode(
    func=sir.model,
    y=state_init,
    times= d, 
    parms=update(params,beta=2)
    # atol = 1e+1, rtol = 1e+1
    # rootfun = rootfun,
    # method="lsodar"
  )
)

@@

The Disease-Free Equilibrium, namely $E_1$, for the above SIR model is given by the solution of the following system:
$S_u+S_n=N0$ and $F_s S_u-\omega S_n=0$.
Let $\tilde{S_u}=N_0/S_u$, the positive solution of the quadratic $$a \tilde{S_u}+b \tilde{S_u}^2+c=0,$$
where $a=\rho$, $b= -\rho+(1-\rho/\omega) \tau W_s$ and $c=-\tau W_s$. Let
  $d = b^2-4ac$, the DFE of the model is

$$S_u^* =N_0 2 a/(-b+\sqrt d), \\ S_n^*=N_0-S_u^* \\ I_j=R_j=0 \ \forall j$$

@@

The Eigenvalues of $G_{11}$, are 0 and $R_0$.
```{r R0}

F_i <- function(params){
   # Returns F_i at DFE 
  unpack(as.list(params))
  Su_dfe<- Su_dfe(params)
  Sn_dfe<- N0-Su_dfe
  sigma <- tau*rho*N0/(tau*(W_s*Su_dfe)+rho*N0) #at DFE 
  return(sigma*W_i)
}

 # just a test
  F_i(params=update(params,rho=0))

R0<-function(params){
    unpack(as.list(params))
    Su_dfe<- Su_dfe(params)
    Sn_dfe<- N0-Su_dfe
    # print(c(Su_dfe,Sn_dfe,Su_dfe+Sn_dfe))
    F_i <- F_i(params) #at DFE

@@

# R0 expression with eta_w/eta_t factored
R02<-function(params){
    unpack(as.list(params))
    Su_dfe<- Su_dfe(params)
    Sn_dfe<- N0-Su_dfe
    F_i <-F_i(params)  #at DFE

@@

Can we recover $R_0=\beta/\gamma$ of the simple SIR? -yes
```{r checkings}
# checking if simple R_0 for SIR can be recovered?
# Case #1: rho=0
all.equal(R0(params=update(params,rho=0)), params[["beta"]]/params[["gamma"]])
# Case #2: 
all.equal(R0(params=update(params,eta_t=1,eta_w=1)), params[["beta"]]/params[["gamma"]])
```

### Contour plot of $R_0=1$ and interpretations approache 1
```{r contour_R0_1, message=FALSE,warning=FALSE }
 # specify the ranges
 beta  <- 0.4  ## set beta high enough to allow R0>1 in worst case
 eta_w <- seq(0,1, length.out=5)
 eta_t <- seq(0.001,0.5, length.out=5) #0.001 to 0.5 
 rho     <- seq(0,0.01, length.out=10)
 omega <- seq(0.001,1 , length.out=10) #note omega must be > rho, was 0.1

 df1 <- expand.grid(N0=params[["N0"]],beta=beta,gamma=params[["gamma"]],omega=omega,rho=rho,
                    W_s=params[["W_s"]],W_i=params[["W_i"]],W_r=params[["W_r"]],
                    P_s=params[["P_s"]],P_i=params[["P_i"]],P_r=params[["P_r"]],
                    eta_w=eta_w,eta_t=eta_t,s=params[["s"]],tau=params[["tau"]])

# Need to be corrected: in F_i, state_dfe should be changed according to the df1!
df2<- data.frame(df1,R0=apply(df1,1,function(params_in)R0(params=params_in)),
                      Fi= apply(df1,1,function(params_in)F_i(params=params_in)))

@@

```{r show_contours_1, width=24,height=24,message=FALSE,warning=FALSE}
p1 <- ggplot(df2,aes(x=omega,y=rho,z=R0))+ theme_bw() +
    theme(panel.spacing=grid::unit(0,"lines"))
(p1
    + geom_contour_filled(breaks=pretty(unique(df2$R0),5),
                          alpha=0.5) ## breaks=0.2)
    + geom_contour(breaks=1,alpha=0.5,colour="black")
    + facet_grid(eta_w~eta_t, labeller=label_special)
    + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_fill_viridis_d(name=parse(text="R[0]"))
)
```

@@

```{r contour_R0_2, message=FALSE,warning=FALSE }
 # specify the ranges
 beta  <- 0.4  
 # eta_w <- seq(0,1, length.out=5) 
 eta_t <- seq(0.001,0.5, length.out=5) #0.001 
 rho     <- seq(0,0.01, length.out=5)
 omega <- seq(0.001,1 , length.out=10) #note omega must be > 0, was 0.1
s <- seq(1,2,length.out=5)

 df11 <- expand.grid(N0=params[["N0"]],beta=beta,gamma=params[["gamma"]],omega=omega,rho=rho,
                    W_s=params[["W_s"]],W_i=params[["W_i"]],W_r=params[["W_r"]],
                    P_s=params[["P_s"]],P_i=params[["P_i"]],P_r=params[["P_r"]],
                    eta_w=params[["eta_w"]],eta_t=eta_t,s=s,tau=params[["tau"]])

df22<- data.frame(df11,R0=apply(df11,1,function(params_in)R02(params=params_in)),
                      Fi= apply(df11,1,function(params_in)F_i(params=params_in)),
                       Su=apply(df11,1,function(params_in)Su_dfe(params = params_in)))
min(df22$Su)
which(df22[]<0)          
```

```{r show_contours_2, width=24,height=24,message=FALSE,warning=FALSE}
p11 <- ggplot(df22,aes(x=omega,y=rho,z=R0))+ theme_bw() +
    theme(panel.spacing=grid::unit(0,"lines"))
(p11
    + geom_contour_filled(breaks=pretty(unique(df22$R0),5),
                          alpha=0.5) ## breaks=0.2)
    + geom_contour(breaks=1,alpha=0.5,colour="black")
    + facet_grid(s~eta_t, labeller=label_special)
    + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_fill_viridis_d(name=parse(text="R[0]"))
)
```

@@

1. $\partial{R_0}/\partial{\eta_t} \geq 0$ and $\partial{R_0}/\partial{\eta_w} \geq 0$.
2. $\partial{R_0}/\partial{\rho} \leq 0$; this is concluded from the Taylor expansion of $R_0$ around $\rho=0$ which is
$R_0 \approx \beta/\gamma + \frac{\beta \rho}{\omega (\omega+\gamma) \gamma^2 W_s} \Big(\gamma(\eta_w-1)(\gamma W_s+\omega W_i) + (\eta_t -1)P_iW_i \omega^2 \Big) + \mathcal{O}(\rho^2)$.
3. Based on the above Taylor expansion around $\rho=0$,
$$\partial{R_0}/\partial{\omega}=  \frac{-\beta \rho}{\gamma W_s\omega^2 (\gamma+\omega)^2}  (a \omega^2 + b \omega + c), $$
where $a=(\eta_w-1)W_i-(\eta_t-1)P_iW_i$, $b=2(\eta_w-1)\gamma W_s$ and $c=(\eta_w-1)\gamma^2 W_s$.
Given that $\eta_t\leq \eta_w$, it is inferred that $a\geq 0$, $b\leq 0$ and $c \leq 0$.
Let $\omega_1<0$ and $\omega_2>0$ be the roots of the quadratic expression in $\partial{R_0}/\partial{\omega}$. Thus, $\partial{R_0}/\partial{\omega}>0$ for $0<\omega<\omega_2$ and  $\partial{R_0}/\partial{\omega}<0$ for $\omega>\omega_2$.

@@

Note that $\eta_t\leq \eta_w$, i.e., reported people have a lower transmission probability than awaiting individuals. The perfect isolation/quarantine occurs when $\eta_w=\eta_t=0$ (see the upper left corner panel). Thus, we only consider the lower-triangle panels in the plot [not sure how to extract them in ggplot?].
(1) Looking at the first column of panels, there seems to be a compensatory relation between $\rho$ and $\omega$. i.e., higher $\rho$ requires smaller $\omega$ to keep R0 lower than 1. Also, for a fixed $\omega$, increasing $\eta_w$ requires higher $\rho$ to achieve the critical R0.
(2) A sensible result that we are expecting is $\partial{R_0}/\partial{\omega}<0$.
